Performance of two different ontological and data access methods

### 2014-07-03 cold2014/magnus.tex
make itemize a wrappable table
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@721 43ef1190-90fd-4dd7-a769-d0121f02b80e

First we wanted to create the planning matrix and
then execute each run as a HTTP post. To do this we needed to make a
small script to calculate the $2^k$ runs and perform the HTTP
posts. We chose to use the programming language \emph{python} to do
this. That was because python was a familiar language and it also had
a package for DoE\footnote{http://pythonhosted.org/pyDOE/}. With the
DoE package we just declared the amount of factors and the matrix was
created.  Further in the script we used the package
\textsf{request}\footnote{http://requests.readthedocs.org/en/latest/}
to do the HTTP posts in python. Below one can see the line of code
executing the request.

\scriptsize\begin{lstlisting}
 r = requests.post('http://localhost:8080/linkedopendata-magnudae/index', 
		  data=payload)
\end{lstlisting}
\normalsize

@@

Before starting the experiments we will present
abbreviations for each factor because their full name made the graphs
totally illegible. The results from all the
experiments can be found in appendix \ref{appD}. %TODO: What to do with the appendix?
\begin{itemize}
  \item Ontology = O
  \item Fuel Type = FT
  \item Transmission = T
  \item Weight = W
  \item Total Weight = WT
  \item Emission = E
  \item Nr. of Gears = G
  \item Seating Capacity = SC
  \item Fuel Consumption = FC
  \item Doors = D
\end{itemize}

@@

\begin{wraptable}{l}{0.35\textwidth}
\vspace{-25pt}
    \begin{tabular}{ | l l |}
    \hline
    {\bf Factors} & {\bf Absolute Effect}  \\ \hline
	  O     & 2.2463476\\ \hline
	  O:T    &0.4536135 \\ \hline
	  O:FT:T &0.4534723 \\ \hline
	  T      &0.4513712 \\ \hline
	  FT:T   &0.4499820\\ \hline
	  O:FT   &0.1240831 \\ \hline
	  FT     &0.1189629 \\ \hline
    \end{tabular}
\caption{Table of effects for the three factor experiment}\label{3factorEffect}
\vspace{-65pt}
\end{wraptable}

\begin{figure}
 \includegraphics[width=12cm, height=8cm]{2factorfinal.pdf}
  \caption{Resulting graph for the three factor experiment}\label{3factorGraph}
\end{figure}

>>>>

First, we created the planning matrix and then executed each run as a
HTTP post. To do this we needed to make a small script to calculate
the $2^k$ runs and perform the HTTP posts. We used the programming
language \emph{Python} with the
DoE\footnote{http://pythonhosted.org/pyDOE/} package.

@@

Before starting the experiments we will present
abbreviations for each factor because their full name made the graphs
totally illegible.

\begin{wraptable}{l}{0.35\textwidth}
    \begin{tabular}{ | l | l |}
    \hline
    {\bf Factor} & {\bf Abbrev} \\ \hline
   Ontology & \textsf{O} \\
   Fuel Type & \textsf{FT} \\
   Transmission & \textsf{T} \\
   Weight & \textsf{W} \\
   Total Weight & \textsf{WT} \\
   Emission & \textsf{E} \\
   Nr. of Gears & \textsf{G} \\
   Seating Capacity & \textsf{SC} \\
   Fuel Consumption & \textsf{FC} \\
   Doors & \textsf{D} \\
\hline
    \end{tabular}
\caption{Factors and their abbreviation}\label{facandabbrev}
\end{wraptable}

@@

\begin{wraptable}{r}{0.35\textwidth}
\vspace{-25pt}
    \begin{tabular}{ | l l |}
    \hline
    {\bf Factors} & {\bf Absolute Effect}  \\ \hline
	  O     & 2.2463476\\ \hline
	  O:T    &0.4536135 \\ \hline
	  O:FT:T &0.4534723 \\ \hline
	  T      &0.4513712 \\ \hline
	  FT:T   &0.4499820\\ \hline
	  O:FT   &0.1240831 \\ \hline
	  FT     &0.1189629 \\ \hline
    \end{tabular}
\caption{Table of effects for the three factor experiment}\label{3factorEffect}
\vspace{-25pt}
\end{wraptable}

\begin{wrapfigure}{l}{0.65\textwidth}
 \includegraphics[width=8.5cm, height=7cm]{2factorfinal.pdf}
  \caption{Resulting graph for the three factor experiment}\label{3factorGraph}
\end{wrapfigure}
